Sparse Representation Approaches for First Stage Retrieval: A Review

### 2021-12-11 src/article.tex
Figure for RepBERT

    \paragraph{Architecture}
    As in BERT\cite{BERT}, the input text is wrapped in [CLS] and [SEP] service marks
    during tokenization:

>>>>

    \paragraph{Architecture}
    \begin{figure}[h]
        \centering
        \includegraphics[scale=0.2]{RepBERT.png}
        \caption{RepBERT architecture}
        \label{fig:RepBERT}
    \end{figure}
    The process of receiving embeddings from document or query sentences is shown
    in the Figure \ref{fig:RepBERT}.

    As in BERT\cite{BERT}, the input text is wrapped in [CLS] and [SEP] service marks
    during tokenization:
